The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

### Research Design
When it comes to public budgeting for education policies, the decision process often does not appear to be rational. That is, it does not seem to take into account the return on investment that should be expected in the long run. Despite this, many claims have been made in the entrepreneurship literature that start-up activities at a country-level are affected by factors other than structural and economic, including cultural and educational. However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.

@@

This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities. Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem (Scott, Dustin, Mertens, Murray, 1996). We will explore further the way this mechanism works. Now, entrepreneurship literature generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009). We intend to show that these individual characteristics are partly shaped at an institutional collective level through the education systems and their staff attitudes.

>>>>

### Research Design
When it comes to public budgeting for education policies, the decision process often does not appear to be rational. That is, it does not seem to take into account the return on investment that should be expected in the long run. Although many claims have been made in the entrepreneurship literature that start-up activities at a country-level are affected by factors other than structural and economic, including cultural and educational. However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.

@@

This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities. Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem (Scott, Dustin, Mertens, Murray, 1996). We will explore further the way this mechanism works. As for entrepreneurship literature, it generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009). We intend to show that these individual characteristics are partly shaped at an institutional collective level through the education systems and their staff attitudes.
